\documentclass[12pt]{article}

\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{textcomp}

\begin{document}
\setlength{\parindent}{0pt}

\def \t {\textrightarrow}
\def \v {\vspace{1em}}
\def \bi {\begin{itemize}}
\def \ei {\end{itemize}}
\def \s[#1] {\section*{#1}}
\def \ss[#1] {\subsection*{#1}}
\def \sss[#1] {\subsubsection*{#1}}

\s[Victorian Age - Recuperare appunti del 30 gennaio]
First reform act said that chidlren had to go to school until 9 \\
Trade-union acts \t established trade unions as legal and permanent organizations \\
Factory acts \t wages are higher and working hours are reduced 

\v

The government financied the Suez canal and colonial expansion in Africa/Asia \\
There was scientific progress  \\
Men were the providers \t and women where expected not to work \\
Prostitution was really popular \t but sex was a taboo \\
Great exhibition of 1851 \t the crystal palace was created, but now it doesn't exist anymore

\ss[Questions]
1 Who had the idea of planning the Great Exhibition? \t it was Victoria's husband (prince Albert) \\
2 What was his aim? \t show britain was top-dog \t political stance \\
3 What is the name of the first item (a technological device) mentioned in the video? What was it used for? \t copying telegraph to reproduce the signal many miles away \t facts simile \\
4 What is the name of the second mentioned item (a wonder)? Where did it come from? \t world largest diamond from India \\
5 What is the name of the third mentioned item (a facility)? What was it like? \t toilets inside the exhibition and public toilets with towels and other things
\end{document}
